Trends of SDR in Thessaloniki 

### 2022-10-05 Article.Rmd
Commit 2022-10-05 17:07

<!-- screening -->
All measurements have been manually screened for inconsistencies and obviously 
problematic data have been excluded.
<!-- physical quantities -->
The conversions to irradiance was done using the calibration factor  .......chp1.... cmp21......
, and adjusting for the dark signal offset daily, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied adjusted for the site,
based on methods of Long and Shi [-@long_automated_2008; -@Long2006].
<!-- Data preparation -->
Due to the large measurement uncertainty near the horizon we exclude all measurements
with SZA greater than $85^\circ$. Moreover, due to nearby hills and buildings
we remove data with azimuth angle between $35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.

@@

<!-- \tiny -->
```{r echo=F, cap="dfsfdffds fs"}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp)
```
<!-- \normalsize -->

>>>>

<!-- screening -->
All measurements have been manually screened for inconsistencies and obviously 
problematic data have been excluded.
<!-- physical quantities -->
The conversions to irradiance was done using the calibration factor  .......chp1.... cmp21......
, and adjusting for the dark signal offset daily, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied adjusted for the site,
based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006].
<!-- Data preparation -->
Due to the large measurement uncertainty near the horizon we exclude all measurements
with SZA greater than $85^\circ$. Moreover, due to nearby hills and buildings
we remove data with azimuth angle between $35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.

@@

<!-- \tiny -->
```{r echo=F, cap="dfsfdffds fs"}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!-- \normalsize -->
